Tables for PM2.5 constituents Paper Manuscript

### 2021-10-17 code/data-analysis/output-cleaning.Rmd
Revision

### Components - SES urban
pmc.1yr.sescat.iqr <- dt.site.urban.ses.cat %>% 
  inner_join(dt.pmc.1yr) %>% 
  group_by(ses.cat) %>% 
  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
  pivot_longer(cols = AS:ZN,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter),
         SES.Cat = substr(ses.cat,1,1)) %>% 
  select(-ses.cat)
```

>>>>

### Components - SES urban
pmc.1yr.sescat.iqr <- dt.site.urban.ses.cat %>% 
  inner_join(dt.pmc.1yr) %>% 
  group_by(ses.cat) %>% 
  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
  pivot_longer(cols = AS:ZN,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter),
         SES.Cat = substr(ses.cat,1,1)) %>% 
  select(-ses.cat)

table.ses <- pmc.1yr.sescat.iqr %>% 
  mutate(IQR = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), IQR, IQR * 1000),
         IQR = sprintf("%0.2f", IQR)) %>% 
  pivot_wider(names_from = "SES.Cat",
              values_from = "IQR",
              names_sort = T) %>% 
  merge(Para.to.Index) %>% 
  rename(Component = Index) %>% 
  select(Component, everything(), -Parameter) %>% 
  filter(Component %in% cmp) %>% 
  mutate(Component = factor(Component, levels = cmp)) %>% 
  arrange(Component) %>% 
  select(Component, L, M, H)

write.csv(table.ses,
          file = here('output','table', 'sescatiqr.csv'))
```

### 2021-10-17 code/data-processors/cms-data-processor.Rmd
Revision

```{r PMC Region}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

>>>>

```{r PMC Region}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN", "K")

@@

```{r}
cmp.major <- c("SI", "NO3", "SO4")

dt.pmc5 <- dt.pmc.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr5", .x, sep = "_"))

dt.pmc4 <- dt.pmc.4yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr4", .x, sep = "_"))

dt.pmc3 <- dt.pmc.3yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr3", .x, sep = "_"))

dt.pmc2 <- dt.pmc.2yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr2", .x, sep = "_"))

dt.pmc1 <- dt.pmc.1yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr1", .x, sep = "_"))

dt.pmc.major <- dt.pmc1 %>% 
  merge(dt.pmc2) %>% merge(dt.pmc3) %>% 
  merge(dt.pmc4) %>% merge(dt.pmc5)

```{r PMC BZ6 - 1-5yr}
dt.ses <- dt.ses.site.bz6 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.pmc.bz6.15yr <- dt.master.ndi.pmc.bz6 %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
  inner_join(dt.pmc.major) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.bz6.15yr, 
          file = here('data', 'processed', 'ndi-pmc-bz6-15yr.csv'),
          row.names = F)
```

```{r PMC BZ 12 - 1-5yr}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.pmc.bz12.15yr <- dt.master.ndi.pmc.bz12 %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
  inner_join(dt.pmc.major) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.bz12.15yr, 
          file = here('data', 'processed', 'ndi-pmc-bz12-15yr.csv'),
          row.names = F)
```

```{r PMC BZ 24 - 1-5yr}
dt.ses <- dt.ses.site.bz24 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.pmc.bz24.15yr <- dt.master.ndi.pmc.bz24 %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
  inner_join(dt.pmc.major) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

view(dt.ndi.pmc.bz24.15yr)
write.csv(dt.ndi.pmc.bz24.15yr, 
          file = here('data', 'processed', 'ndi-pmc-bz24-15yr.csv'),
          row.names = F)
```

### 2021-10-17 code/data-viz/forest-plots-color-shape.Rmd
Revision

```{r set theme 4 - matrix plots}
ggtheme.matrix <- theme_bw() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 9, color = 'black'),
        legend.position = 'right',
        legend.title = element_blank(),
        legend.text = element_text(size = 9, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')
  )
```

@@

@@

So.main <- c("Steel", "Oil", "Salt", "Coal", 
         "Biomass", "Traffic", "Metals", "Soil")
So.multi <- c("Soil", "Metals", "Traffic",
              "Coal", "Oil")

@@

@@

@@

>>>>

```{r set theme 4 - components - effect modification, subgroups, multiple groups plots}
ggtheme.multi.3 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.5,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0,0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title.x = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 5 - matrix plots}
ggtheme.matrix <- theme_bw() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 9, color = 'black'),
        legend.position = 'right',
        legend.title = element_blank(),
        legend.text = element_text(size = 9, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')
  )
```

@@

cuz.g.abs <- c("All-Cause", "Cardiovascular", "Respiratory", "Lung Cancer")

@@

So.main <- c("Steel", "Oil", "Salt", "Coal", 
         "Biomass", "Traffic", "Metals", "Soil")

So.multi <- c("Soil", "Metals", "Traffic",
              "Coal", "Oil")

@@

# Ghraphical Abs
```{r - Factor SES-Adj, fig.dim = c(7.5, 6.5)}
data <- out.fac.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz.g.abs) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

p <- ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
    geom_vline(xintercept = 1, linetype = 2, color = "black") +
    geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
                 color = plot.cols, size = 0.25, show.legend = F) + 
    geom_point(aes(x = HR, y = Index, shape = sig), 
               color = plot.cols, size = 1.5, show.legend = F) +
  labs(x = "HR (95% CI) per IQR Increase", y = expression(paste("Source-Related ", PM[2.5])),
       title = expression(paste("Association of Long-Term Source-Related ", PM[2.5], " Exposure and Cause-Specific Mortality"))) +
    scale_shape_identity() +
    facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
   theme_bw() + 
    theme(panel.spacing.x = unit(0.5, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title = element_text(size = 12, color = 'black'),
        axis.text = element_text(size = 9, color = 'black'),
        plot.title = element_text(size = 12, face = 'bold', color = 'black', hjust = 0.5, vjust = 2))

annotate_figure(p, 
                bottom = text_grob(expression(paste("IQRs in μg/",m^3, ": Soil = 0.29, Metals = 0.07, Traffic = 4.09, Biomass = 0.13, Coal = 4.36, Salt = 0.03, Oil = 0.03, Steel = 0.03")), size = 8)) + 
  ggsave(here('output','plot','graphical-abstract.jpeg'), width = 9.5, height = 4, dpi = 600)
```

@@

### Components Region
```{r - Components Region, fig.dim = c(7.5, 8.5)}
data <- out.pmc.region %>% 
  filter(Index %in% c(cmp.multi, "K"),
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = c(cmp.multi, "K")),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- c(cmp.multi.labels, "K")

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.3, n = 1) +
ggsave(here('output', 'plot','pmc-region-with-K.jpeg'), width = 7.5, height = 9.5, dpi = 600)
```

@@

### Factors Region
```{r - Factor Region, fig.dim = c(7.5, 6.5)}
data <- out.fac.region %>% 
  filter(Index %in% c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Oil"),
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Oil")),
  Tag = ifelse(Region == "west", "d",
               ifelse(Region == "midwest", "c",
                      ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.integer(sig)
  )

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-region-with-Biomass.jpeg'), width = 7.5, height = 7.5, dpi = 600)
```

### 2021-10-17 code/data-viz/manuscript-tables.Rmd
Revision

load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
load(here('output','analysis','out-pmc-buffer-expo.RDa'))
```

@@

@@

```{r}
print(doc, target = here('output','table','supplement-tables-revision.docx'))
```

>>>>

load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-sescat-upd.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
load(here('output','analysis','out-pmc-buffer-expo.RDa'))
```

@@

### Figure 11 - constituents SES-urban - updated
```{r}
out.pmc.sescat.upd <- out.pmc.sescat.upd %>% 
  mutate(SES.Cat = ifelse(SES.Cat == "L", "Low",
                          ifelse(SES.Cat == "M", "Middle", "High")),
         SES.Cat = factor(SES.Cat, levels = c("Low", "Middle", "High")))

doc <- Table.Multi.sescat(dt = out.pmc.sescat.upd, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by income category in urban areas.", ftnt = "Continued ...")
doc <- Table.Multi.sescat(dt = out.pmc.sescat.upd, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by income category in urban areas., Continued", ftnt = "")
```

@@

```{r}
print(doc, target = here('output','table','supplement-tables-revision-sescatupd.docx'))
```
